---
title: "International Vistor Arrivals Statistics - `r format(Sys.Date(), '%B %Y')` Highlights"
output: 
  word_document: 
    reference_docx: styles_reference.docx #including the logos
---

```{r setup, include=FALSE}
# Set echo=FALSE as default for code cells
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      dpi = 600)
```


```{r preparation, include = FALSE}
# Load the required libraries
library(knitr) # Creating documents
library(flextable) # Nicely formatted tables
library(rnaturalearth) # World map
library(sf) # Working with spatial data
library(ggplot2) # Creating plots
library(dplyr) # Working with data
library(tidyr) # For pivoting data.frames
library(janitor) # Adding row and column totals

# Set the table formatting defaults
set_flextable_defaults(font.family="Times New Roman", font.size=5, font.color="black",
                       text.align="left", table.layout="fixed", theme_fun="theme_booktabs")

# Note where VNSO code/data is on current computer
repository <- file.path("..", "..")

# Note the open data path
openDataFolder <- file.path(repository, "data", "open")

# Note the secure data path
secureDataFolder <- file.path(repository, "data", "secure")

# Note the output data path

outputDataFolder <- file.path(repository, "outputs")

# Some general ggplot settings
plotTextSize <- 9
xAxisText <- list(
  "angle" = 35,
  "size" = plotTextSize,
  "vjust" = 1.1,
  "hjust" = 1
)
```


```{r load data}

# Load the processed trade statistics for month of interest
# Read in the processed TOURISM data from output folder of the repository 

tourismProcessedFile<- file.path(outputDataFolder, "OUT_PROC_Clean_Example.csv")
tourismProcessed <- read.csv(tourismProcessedFile, header = TRUE, na.strings = c("","NA","NULL","null"))

# Read in the previously published historical TOURISM data from output folder of the repository 

tourismHistoricFile<- file.path(outputDataFolder, "SEC_OUT_HIST_DATA.csv")
tourismHistoric <- read.csv(tourismHistoricFile, header = TRUE, na.strings = c("","NA","NULL","null"))

```


# National Sustainable Development Plan Indicators (NSDP)- Table

```{r NSDP indicators}
### Calculating NSDP Indicators

# ECO 3.2.1 Average annual household income from tourism
x <- 200

# ECO 3.2.2 Annual change in tourism by air and sea arrivals
y <- 100

# ECO 3.2.3 Proportion of visitors traveling to outer islands
z <- 50

```


```{r NSDP table}

# Create the NSDP table

nsdpIndicators <- data.frame(
  "Policy Objectives"=c("ECO 3.2: Deepen the integration of the tourism sector into the rural economy to spread opportunities to rural communities"),
  "SMART Indicators"=c("ECO 3.2.1 Average annual household income from tourism",
                       "ECO 3.2.2.Annual change in island tourism by air and sea arrivals",
                       "ECO 3.2.3 Proportion of visitors
traveling to outer islands"),

  "Indicator Value"= c(
    x,
    y,
    z
  ),check.names=FALSE, stringsAsFactors=FALSE)


# Round the indicator values
nsdpIndicators$`Indicator Value` <- round(nsdpIndicators$`Indicator Value`, digits = 2)

# Initialize a flextable object for NSDP table
indicatorsTable <- flextable(nsdpIndicators)

# Add a header row and set background colour
indicatorsTable <- bg(indicatorsTable, bg="coral1", part="header")

# Set the vertical alignment to top
indicatorsTable <- valign(indicatorsTable, valign="top", part="all")

# Merge repeated values in the Policy Objectives column
indicatorsTable <- merge_v(indicatorsTable, j = "Policy Objectives")

# Set table width to 100%
indicatorsTable <- set_table_properties(indicatorsTable, width=1, layout="autofit")

# Set the theme
indicatorsTable <- theme_booktabs(indicatorsTable)

# Print table
indicatorsTable
```
 
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  


# International Visitor Arrivals 10 year monthly trend by Air and Cruise, December 2009 - December 2019- Line Graph


```{r visitors arrivals through time, fig.height=5, fig.width = 15}
# Calculate value of visitors by Air and Cruise for current month for historical data

### The following needs a value for "currentMonth" - needs either setting as a value or extracting from data
VisitorsValue <- tourismHistoric %>%
  filter(Month == currentMonth)

# Create a line graph
ggplot(data = VisitorsValue, aes(x = Year, y = Value, group = Visitor.Arrivals)) +
  geom_line(aes(color = Visitor.Arrivals), size = 1.5, alpha = 0.75) +
  labs(y = "Number of Visitors") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = xAxisText$angle,
                                   vjust = xAxisText$vjust, 
                                   hjust = xAxisText$hjust, 
                                   size =xAxisText$size),
        axis.title.y = element_text(size = plotTextSize),
        axis.title.x = element_blank(),
        legend.title = element_text(size = plotTextSize))

```


# Sex by Type of Passsenger- Bar Chart

```{r main reasons for visiting Vanuatu, warning=FALSE, fig.width=5.5, fig.height=2.5}



```


# Visitor Arrivals by Usual Country of Residence- Map

```{r country orginating from, warning=FALSE, fig.width=5.5, fig.height=2.5}

## Getting latest statistics ##

countryVistorsGrouped <- tourismProcessed %>%
  filter(port %in% c("SAIR","SAIRP","VAIR","VAIRP"))%>%
  filter(visitor_resident %in% ("Visitor"))%>%
  filter(arr_depart %in%("ARRIVAL"))%>%
  group_by(visiors_by_region) %>%
  count() %>%
  arrange(desc(n))

colnames(countryVistorsGrouped)[1] <- "Country"

# Get the polygons for the world
world <- rnaturalearth::ne_countries(type = "countries", scale = "medium", returnclass = "sf")

# Merge in my example data
world <- merge(world, countryVistorsGrouped, by.x = "admin", by.y = "Country", all.x = TRUE)

# Plot with ggplot
ggplot(data = world) +
  geom_sf(aes(fill = n)) + 
  guides(fill=guide_legend(title="Visitor Arrivals by Usual Country of Residence\n(number)")) +
  theme(legend.title = element_text(size = 9))

```


# Age by Country of Usual Residence- Table (group ages by country)

```{r main islands tourists visit in Vanuatu, warning=FALSE, fig.width=5.5, fig.height=2.5}



```


# Visitor Arrivals Purpose of Visit- Infographic (main reasons are holiday, buinsess, visiting friends)

```{r main reasons for visiting Vanuatu, warning=FALSE, fig.width=5.5, fig.height=2.5}



```


# Proportion of Visitors to Outer Islands- Bar Chart 

```{r main islands tourists visit in Vanuatu, warning=FALSE, fig.width=5.5, fig.height=2.5}



```

